INSTRUCTION SETS FOR STRANGERS

### 2021-09-13 instructionsetsforstrangers/instructionsetsforstrangers.tex
part II

\documentclass[11pt]{report}
\usepackage{geometry}
\geometry{letterpaper, top=1in, bottom=1in, left=1in, right=1in}                                 
\usepackage[parfill]{parskip}   
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{array}
\usepackage{tabularx}
\setlength{\parindent}{0em}
\pagenumbering{gobble}

@@

\title{INSTRUCTION SETS FOR STRANGERS -- PART I}
\date{}

\begin{document}
\maketitle
%\tableofcontents
%----------------------------------------------
\section*{Location Choice}

@@

\begin{figure}[ht]
\centering
\includegraphics[scale=0.10, angle=270]{"images/crosswalk_nopeople.jpg"}
\caption{The selected crosswalk on 17th st.}
\label{fig:nopeople}
\end{figure}

@@

\section*{Initial Observation}

@@

\begin{figure}[ht]
\centering
\includegraphics[scale=0.8]{"images/ms1_aeiou.png"}\\
\vspace{0.5cm}
\includegraphics[scale=0.8]{"images/ms1_behaviormap.png"}
\caption{AEIOU and Behavior mapping exercise}
\label{fig:behaviormap}
\end{figure}

@@

\section*{Ideation}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=1.4\textwidth, angle=90]{"images/ms1_brainstorming.png"}
\caption{Results of brainstorming activity.}
\label{fig:brainstorm}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[scale=0.08]{"images/wavemachine_overlay_2.jpg"}
\caption{Sketch of device on location.}
\label{fig:overlay}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[scale=0.6]{"images/wavemachine_sketch.png"}
\caption{Possible mechanical design of device.}
\label{fig:sketch}
\end{figure}

>>>>

\documentclass[11pt]{report}
\usepackage{geometry}
\geometry{letterpaper, top=1in, bottom=1in, left=1in, right=1in}                                 
\usepackage[parfill]{parskip}   
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{array}
\usepackage{tabularx}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan
    }

\setlength{\parindent}{0em}
\pagenumbering{gobble}

@@

\title{INSTRUCTION SETS FOR STRANGERS}
\date{}
\author{Lauria Clarke}

\begin{document}
\maketitle
%\tableofcontents
%----------------------------------------------
\section*{PART I - Ideation}
\subsection*{Location Choice}

@@

\begin{figure}[ht]
\centering
\includegraphics[scale=0.10, angle=270]{"images/I/crosswalk_nopeople.jpg"}
\caption{The selected crosswalk on 17th st.}
\label{fig:nopeople}
\end{figure}

@@

\subsection*{Initial Observation}

@@

\begin{figure}[ht]
\centering
\includegraphics[scale=0.8]{"images/I/ms1_aeiou.png"}\\
\vspace{0.5cm}
\includegraphics[scale=0.8]{"images/I/ms1_behaviormap.png"}
\caption{AEIOU and Behavior mapping exercise}
\label{fig:behaviormap}
\end{figure}

@@

\subsection*{Ideation}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=1.4\textwidth, angle=90]{"images/I/ms1_brainstorming.png"}
\caption{Results of brainstorming activity.}
\label{fig:brainstorm}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.8\textwidth]{"images/I/wavemachine_overlay_2.jpg"}
\caption{Sketch of device on location.}
\label{fig:overlay}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.8\textwidth]{"images/I/wavemachine_sketch.png"}
\caption{Possible mechanical design of device.}
\label{fig:sketch}
\end{figure}

\clearpage
\section*{PART II - Iteration}
\subsection*{prototyping}

The initial prototype was extremely quick. It successfully proved that the basic mechanism did, in fact work. \href{https://drive.google.com/file/d/1A-JF5d3mOUxOp_nL0GExQ2gzeuzpgY3x/view?usp=sharing}{Link to video of initial prototype.}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.8\textwidth, angle=-90]{"images/II/prototype_1.JPG"}
\caption{Initial prototype.}
\end{figure}

The initial prototype required improvement in four areas; a more solid connection between the arm and the base, a way for the base to be connected to a street post securely, improved elastic, and an eye catching handle.

Using a bolt and some washers the arm and the base were connected in a way that allowed the arm to swing freely without twisting. Next, in order to mount the wave machine, we found some large zip ties and drilled holes in the base to thread the zip ties through. During this process we discovered that making the mechanism one-sided decreased the complexity of the device and made it easier to mount the base. By restricting the movement to be one-sided we also decreased the chance of the arm becoming stuck in either direction. Despite the reduction in range, it was still quite satisfying to use the mechanism. As we played with the movement of the arm, the easiest elastics on hand were hair-ties. By trying a couple different sizes we honed in on the best tension for the weight of the arm. Finally, we cut the end off of an aluminum mop and colored it bright red with a sharpie in the hope that this would grab someone's attention. \href{https://drive.google.com/file/d/10h-Otp0xxu8sbUBII9ftw7f-XZoaok2H/view?usp=sharing}{Link to video of second prototype.}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.8\textwidth, angle=-90]{"images/II/prototype_2.JPG"}
\caption{Initial prototype.}
\end{figure}

\subsection*{testing results}

Due to time constraints, we chose to test the wave machine close to home instead of at the proposed site. Installation went well; it was easy to attach the base securely to the street post and then adjust it to be out of the way of the crosswalk signals. Pulling the handle was satisfying and the motion of the mechanism was smooth and effective. It was fairly visible from across the street when the arm was waving. \href{https://drive.google.com/file/d/1Gzw53p0xpSqZ-RktlmBlWZ7QyR_WPB5E/view?usp=sharing}{Link to video of installed protptype.}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth, angle=-90]{"images/II/install_closeup.JPG"}
\includegraphics[width=0.5\textwidth, angle=-90]{"images/II/install_closeup_2.JPG"}
\caption{Installed mechanism.}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.8\textwidth, angle=-90]{"images/II/install_far.JPG"}
\caption{Installed mechanism.}
\end{figure}

Unfortunately, while the chosen time and location yielded a high degree of foot traffic, few noticed the wave machine. A few people looked at it, but no one pulled the handle. One person waved back at us while we were using the machine and a few others smiled. Other than that, the initial testing was successful for mechanical refinement, but not so much for user feedback.

\subsection*{next steps}

It was clear after initial testing that the wave machine needed to be more noticeable and the chosen location needed to be more heavily trafficked by individuals out looking for fun. In addition to making the mechanism robust enough to stand up to real use, three modifications were decided upon: improved location, more visible arm, more alluring handle.

We happened to witness a particular crosswalk that was very crowded on both sides late at night. Nearly all of the people on both sides of the street were going to or from bars and were already pretty intoxicated. Many people near the crosswalk were waiting in line to enter various bars. Other than trying to get to the line, none of these people were in a particular rush.

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{"images/II/elwire.jpg"}
\caption{Electroluminescent wire.}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.8\textwidth]{"images/II/essex_magicianbar.JPG"}
\\
\includegraphics[width=0.8\textwidth]{"images/II/essex_opposite.JPG"}
\caption{Nightlife on both sides of proposed crosswalk.}
\end{figure}

Using electroluminescent (EL) wire we planned to increase the visibility of the arm. The EL wire would be placed around the outline of the arm and hand and could be set to be constantly on, or to blink. In addition to grabbing peoples attention, this would create an interesting visual effect as the arm waved through the air.

Lastly, the handle needed to be improved upon. To make it appealing at night we though it would be a good idea to have it light up and blink.

\clearpage
\section*{PART III - Installation}
